GEE models

### 2016-05-02 doc/gee.Rmd
Minor edit to YAML gee.Rmd
Included sensitivity analysis for TAG/BaseTAG

---
title: "GEE models"
author: "Luke W. Johnston"
output: 
    rmarkdown::html_vignette:
        keep_md: true
        toc: true
---

@@

outcomes <- c('linvHOMA', 'lISI', 'lIGIIR', 'lISSI2')
outcomes_is <- c('linvHOMA', 'lISI')
outcomes_bcf <- c('lIGIIR', 'lISSI2')
ne_pct <- grep('^pct_ne', names(gee_df), value = TRUE)
ne_conc <- c('TotalNE', grep('^ne\\d\\d', names(gee_df), value = TRUE))
covariates0 <- c('VN')
covariates_is <- c('VN', 'Waist', 'Sex', 'Ethnicity', 'BaseAge', 'ALT')
covariates_bcf <- c('VN', 'Waist', 'Sex', 'Ethnicity', 'BaseAge', 'ALT', 
                    'MET', 'AlcoholPerWk')
covariates_is_tag <- c('VN', 'Waist', 'Sex', 'Ethnicity', 'BaseAge', 'ALT', 'TAG')
covariates_bcf_tag <- c('VN', 'Waist', 'Sex', 'Ethnicity', 'BaseAge', 
                        'ALT', 'MET', 'AlcoholPerWk', 'TAG')
```

@@

```{r geeResults_IS_int}
gee_results_is_int <- bind_rows(
    analyze_gee(gee_df, outcomes_is, ne_pct, covariates_is, 'mol%', adj.p = TRUE, int = TRUE),
    analyze_gee(gee_df, outcomes_is, ne_conc, covariates_is, 'nmol/mL', adj.p = TRUE, int = TRUE),
    analyze_gee(gee_df, outcomes_is, ne_pct, covariates_is_tag, 'mol% (w/ tag)', adj.p = TRUE, int = TRUE),
    analyze_gee(gee_df, outcomes_is, ne_conc, covariates_is_tag, 'nmol/mL (w/ tag)', adj.p = TRUE, int = TRUE)
    ) %>% 
    tidy_gee_results()
gee_results_is_int %>%
    select(p.value) %>% 
    plot()
```

@@

```{r geeResults_BCF_int}
gee_results_bcf_int <- bind_rows(
    analyze_gee(gee_df, outcomes_bcf, ne_pct, covariates_bcf, 'mol%', adj.p = TRUE, int = TRUE),
    analyze_gee(gee_df, outcomes_bcf, ne_conc, covariates_bcf, 'nmol/mL', adj.p = TRUE, int = TRUE),
    analyze_gee(gee_df, outcomes_bcf, ne_pct, covariates_bcf_tag, 'mol% (w/ tag)', adj.p = TRUE, int = TRUE),
    analyze_gee(gee_df, outcomes_bcf, ne_conc, covariates_bcf_tag, 'nmol/mL (w/ tag)', adj.p = TRUE, int = TRUE)
    ) %>% 
    tidy_gee_results()
gee_results_bcf_int %>% 
    select(p.value) %>% 
    plot()
```

>>>>

---
title: "GEE models"
author: "Luke W. Johnston"
output: 
    rmarkdown::html_vignette:
        toc: true
---

@@

outcomes <- c('linvHOMA', 'lISI', 'lIGIIR', 'lISSI2')
outcomes_is <- c('linvHOMA', 'lISI')
outcomes_bcf <- c('lIGIIR', 'lISSI2')
ne_pct <- grep('^pct_ne', names(gee_df), value = TRUE)
ne_conc <- c('TotalNE', grep('^ne\\d\\d', names(gee_df), value = TRUE))
covariates0 <- c('VN')
covariates_is <- c('VN', 'Waist', 'Sex', 'Ethnicity', 'BaseAge', 'ALT')
covariates_bcf <- c('VN', 'Waist', 'Sex', 'Ethnicity', 'BaseAge', 'ALT', 
                    'MET', 'AlcoholPerWk')
covariates_is_tag <- c('VN', 'Waist', 'Sex', 'Ethnicity', 'BaseAge', 'ALT', 'BaseTAG')
covariates_bcf_tag <- c('VN', 'Waist', 'Sex', 'Ethnicity', 'BaseAge', 
                        'ALT', 'MET', 'AlcoholPerWk', 'BaseTAG')
```

@@

```{r geeResults_IS_int}
gee_results_is_int <- bind_rows(
    analyze_gee(gee_df, outcomes_is, ne_pct, covariates_is, 'mol%', adj.p = TRUE, int = TRUE),
    analyze_gee(gee_df, outcomes_is, ne_conc, covariates_is, 'nmol/mL', adj.p = TRUE, int = TRUE),
    analyze_gee(gee_df, outcomes_is, ne_pct, covariates_is_tag, 'mol% (w/ tag)', adj.p = TRUE, int = TRUE),
    analyze_gee(gee_df, outcomes_is, ne_conc, covariates_is_tag, 'nmol/mL (w/ tag)', adj.p = TRUE, int = TRUE)
    ) %>% 
    tidy_gee_results()
gee_results_is_int %>%
    select(p.value) %>% 
    plot()
gee_results_is_int %>%
    .$p.value %>% 
    min()
```

@@

```{r geeResults_BCF_int}
gee_results_bcf_int <- bind_rows(
    analyze_gee(gee_df, outcomes_bcf, ne_pct, covariates_bcf, 'mol%', adj.p = TRUE, int = TRUE),
    analyze_gee(gee_df, outcomes_bcf, ne_conc, covariates_bcf, 'nmol/mL', adj.p = TRUE, int = TRUE),
    analyze_gee(gee_df, outcomes_bcf, ne_pct, covariates_bcf_tag, 'mol% (w/ tag)', adj.p = TRUE, int = TRUE),
    analyze_gee(gee_df, outcomes_bcf, ne_conc, covariates_bcf_tag, 'nmol/mL (w/ tag)', adj.p = TRUE, int = TRUE)
    ) %>% 
    tidy_gee_results()
gee_results_bcf_int %>% 
    select(p.value) %>% 
    plot()
gee_results_bcf_int %>%
    .$p.value %>% 
    min()
```
